  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%  MURK %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\mysubsection{Murk Virtues}{advancement-murk-virtues}

\begin{center}
\myredbold{Unless otherwise specified, you can only take each Virtue once.}
\end{center}

  \mytable{Y Y Y} {
    \thead{Daredevil (Level 2+)} & \thead{Heroic (Level 4+)} & \thead{Legendary (Level 7+)} \\
  } {
    Apprentice of the Bride & Footpad of the Bride & Kismet III \\
    Ghost & Invisibility & Loner \\
    Kismet I &  Kismet II &  Personality III \\
    Mortal Charms & Personality II  &  Saves III \\
    Personality I & Saves II & Sharper of the Bride \\
    Saves I & Self-Reliant & Stonewalker\\
    Self-Sufficient & Shadowblade & -  \\
    Stonespeaker & Stoneshaper & - \\
    Will to Live  & - & - \\
    You and Me  & -  & - \\
}



\begin{multicols*}{2}

\myhighlight{Apprentice of the Bride}{adv-murk-bride}

Advance \mylink{Whispers of the Bride}{vulgate-whisper-the-bride} from Untrained to Apprentice (d4) rank.

\myhighlight{Footpad of the Bride}{adv-murk-footpad}

Advance \mylink{Whispers of the Bride}{vulgate-whisper-the-bride} from Apprentice to Footpad (d6) rank.


\myhighlight{Ghost}{adv-murk-ghost}

Mortals tend to forget you're there. They can never seem to remember your face (though they'll remember "a shadowy figure" of some sort); they don't speak to you unless you speak first, you tend to startle them when you come up to them. This means that \mybold{if (and only if) a Mortal is alone}, you can come right up to them and put a hand on their shoulder (or a knife in their back) without them noticing you're there (meaning you would get \mylink{the Drop}{combat-drop} on them). 

\myhighlight{Invisibility}{adv-murk-invisibility}

Once per Session, you can step into a shadow and become \mylink{Invisible}{effect-invisible}.  You can use this to get \mylink{the Drop}{combat-drop} on someone, but there must be a shadow present (you couldn't do this in the middle of a sunny field, for example).

\myhighlight{Kismet I-III}{adv-murk-kismet}

Advance \mybold{all} aspects of your \mylink{Kismet}{adventurer-kismet} to the next named level (\DEATH, \INJURY, or \INSANITY).

\myhighlight{Loner}{adv-murk-loner}

Gain +4 \MAX Grit. Once per Session, if you are completely by yourself, you can treat a \mylink{Breather}{combat-resting-breather} as if you had taken a \mylink{Bivouac}{combat-resting-bivouac}. You must make your Provisions roll if applicable. 

\myhighlight{Mortal Charms}{adv-murk-mortal-charms}

You can perform the \mylink{Charms}{vulgate-charms} Vulgate at will.

\myhighlight{Personality I-III}{adv-murk-personality}

Advance two \mybold{different} aspects of your \mylink{Personality}{adventurer-personality} \DCUP.

\myhighlight{Saves I-III}{adv-murk-saves}

Advance \mybold{all} \mylink{Saves}{adventurer-saves} to the next named level (Defenseless to Preserved; Preserved to Protected; etc).

\myhighlight{Self-Reliant}{adv-murk-self-reliant}

Gain +4 \MAX Grit. Restore an additional +4 Grit when you take a \mylink{Breather}{combat-resting-breather} up to your \MAX, unless a \mylink{Injury}{adventurer-kismet-injury} prevents you from doing so).


\myhighlight{Self-Sufficient}{adv-murk-self-sufficient}

Gain +4 \MAX Grit. You never need to roll \mylink{Provisions}{gear-equipment} when taking a \mylink{Bivouac}{combat-resting-bivouac}.

\myhighlight{Shadowblade}{adv-murk-shadowblade}

You can reach into a shadow and pull out a long, ebony dagger that appears to be made of black vapor. The weapon exists for as long as it is not exposed to sunlight.  The dagger is magical and does d10 damage, and can have Toxins applied to it.  If the dagger takes a life it immediately disappears into the Void, bearing the soul of the slain creature with it forever.

\myhighlight{Sharper of the Bride}{adv-murk-sharper}

Advance \mylink{Whispers of the Bride}{vulgate-whisper-the-bride} from Footpad to Sharper (d8) rank.

\cbreak

\myhighlight{Stoneshaper}{adv-murk-stone-shaper}

Once per Session, you can speak to stones and have them reshape themselves.  The stones can't be bigger than 3m in any dimension.  The stone will reshape itself into anything you desire - a large rock could be shaped into an idol, a passage could be made through a wall (provided the wall was less than 3m thick).  The object created is rough-hewn - fine detail isn't possible (Arbiter's discretion)


\myhighlight{Stonespeaker}{adv-murk-stone-speaker}

In addition to the \mylink{Silent Speech}{idiolect-silent-speech}, you can convince the stones to move by speaking with them for Minutes. They can't do anything rocks wouldn't be able to do (float on water, fly through the air without being thrown, etc.), but you can convince them to roll, "walk", fall, or move out of the way.

\myhighlight{Stonewalker}{adv-murk-stonewalker}

Once per Session, you can travel through stone or earth up 10km away. You need to have visited the destination and there must be uninterrupted stone or ground between yourself and the destination. You can travel this distance in Minutes. When you reach level 9, you can use this ability to return to \mylink{Svartalfheim}{species-murk} if you choose (retiring your character).

\myhighlight{Will to Live}{adv-murk-will-to-live}

You only fail your \DEATH try on a 1 (instead of a 1 or 2).

\myhighlight{You and Me}{adv-murk-you-and-me}

When fighting a single combatant, you gain +4 damage and a +4 bonus to any \mylink{Combat Actions}{combat-combat-actions} provided there is no one else Close to you (Ally or Monster). This bonus immediately ends if any additional Ally or Monster comes Close to you, and won't return for the rest of Combat.

\end{multicols*}
