\mysection{Burden}{gear-burden}

  \ed{To the best of my knowledge, the original concept of Significant and Insignificant items come from Logan Knight's "In Corpathium".

  Encumbrance; hindrance; weight; load; etc. Whatever you call it, it seems that games have been trying to figure out how to limit how much weight an Adventurer can carry since Gygax first put pencil to paper.  Too much and it feels like algebra homework, too little and you have munchkins bristling with dozens of axes.  

  Hopefully this is the sweet spot.
}

  Your \mybold{Burden} is a single number that represents how hard it might be to carry something. 

  Things you are carrying are divided into "insignificant" and "significant" items. We don't \myital{really} care about those trivial, insignificant items; as long as you can say you've put it in a reasonable place and can describe that place to the Arbiter, the item has no Burden. For instance, you could tell the Arbiter "I've got the 11 weird rocks we've found at the bottom of my backpack, the amulet is tied to my belt, and I stowed the matches in my pocket", but balancing the rocks on your head or stuffing the amulet in a ... place ... might get vetoed. The Arbiter has final say whether or not something is trivial and whether or not you've stored these items in a reasonable place.

  The only thing that matters are "significant" items, which are represented by their Burden. Armor and swords and shields have a Burden rating, as do things that are heavy (like an anvil); unwieldy (a 3 meter pole); or inhibiting (if you were cursed with Obesity or Weakness, this might be represented as "extra" significant items you're carrying, or by being able to carry fewer significant items, respectively). Certain large items might have a Burden that can be "shared" by others at the Arbiter's discretion - for example, a large carpet might have a Burden of 12, but two or more people can help carry it and divide up the Burden amongst themselves.

  The \MAX Burden you can carry is your \VIG + 2 i.e. if you have a d10 \VIG, your Burden is 12. \mylink{Pooka}{species-pooka} and \mylink{Night Children}{species-night-child} don't get the +2 bonus, because they're Tiny - they can only carry their \VIG in Burden. If you're carrying your \MAX Burden, you're morbidly encumbered and you can only shuffle around, and you can't make \mybold{any} \RO or \RB tries until you drop something.

Some general Burdens you may encounter:

\callout {
  \mybullet {
    \item 2h weapons have a Burden of 2; 1h weapons have a Burden of 1; \OneHalf handed weapons have a Burden of \OneHalf.
    \item Armor: Light has a Burden of 1; Armor: Medium has a Burden of 2; Armor: Heavy has a Burden of 3. Shields have a Burden of 1.
    \item 4kg worth of coins counts as 1 Burden. A person counts as 100kg (25 Burden), but Pooka and Night Children are only 15.
  }
}

  \example {
    Andre Preneur, assassin for hire, carries out his contracts with two daggers sheathed in a small poison-filled bladder on his back (1) and carries a Grappling Hook (1) and 25m of rope (1).  His Burden is 3.

    \myskip


    Balthazar the Breathtaking carries a Polearm (2) and wears a bandolier of 4 daggers (1. The bandolier halves the value of the daggers).  He's got a big bag full of rat fur, but the Arbiter rules this as not significant.  His Burden is 3.

    \myskip

    The Nightie Knight uses a Sword (1), a Shield (1), and wears Heavy armor (which has a Burden of 0 because she has the Sellsword Virtue \mylink{Second Skin}{sellsword-virtue-second-skin}).  She carries a Strongbow on her back (2) with a Quiver on her hip (1).  Her Burden is 5.
  }

