\mysection{Services}{gear-services}


  Unless the Arbiter says otherwise, all Small, Medium, and Large Settlements have any of these basic services:

  \mybold{Traders} sell various \mybold{Tools} of the trade and other common items;

  \mybold{Hunters and Leatherworkers} sell and repair Light Armors, slings, and bows;

  \mybold{Ironmongers} sell and repair Medium and Heavy Armors, and sell Weapons  appropriate to the size of the Settlement (see the section on \mybold{Repairing Armor} below);

  \mybold{Black marketeers and Apothecaries} sell Narcotics; 


  \mybold{Mundunugu} can summon Hekaphage to eat Curses (see the section on the \mylink{Hekaphage}{occultism-hekaphage} under \mypg{Occultism}{cunning-occultism} for costs);


   \mybold{Chirugeons} can heal \mylink{Beatings}{physical-wound-beating}, \mylink{Addictions}{gear-narcotics-addiction}, \mylink{Diseases}{vulgate-medicine-diseases}, or \mylink{Madness!}{injury-insanity-madness} for 500 \AG per trauma removed.


More esoteric goods (specific components, rare or complex objects, magical items, etc.) should only be available through \mylink{Side Stories}{downtime-side-story} - or be adventures unto themselves!

\mysubsection{Libraries}{gear-services-library}

Libraries are occasionally found in Medium Settlements, always found in Large Settlements, and almost never found in Small Settlements (there are always exceptions!). A library is required to perform certain types of \mypg{Research}{research}.

\mysubsection{Loci}{gear-services-loci}

The \myital{locus discordiae}, known collectively as Loci, are places of \mypg{Unhallowed Earth}{occultism-unhallowed-earth} located in Settlements (similar to Libraries above).  They can be found in Settlements of any size.  These places are usually located off the beaten path - in crypts, abandoned buildings, slums, etc. and are often the property of \myital{Mundunugu} - mystics who summon Hekaphage to eat various kinds of Curses. Depending on the Settlement, these loci can either be embraced, tolerated, or stomped out whenever found by the powers that control the village, town, or city. 

\mysubsection{Shrines}{gear-services-shrines}

Shrines are places of \mypg{Hallowed Ground}{miracle-hallowed-ground} located in Settlements (similar to Libraries above), consecrated to a specific Small God. There is a base 1-in-6 chance that a Small Settlement has a specific Shrine; a 3-in-6 chance in a Medium Settlement; and a 5-in-6 chance in a Large Settlement (the Arbiter should override this as she sees fit!)


\mysubsection{Repairing Armor}{gear-armor-repair}

Your Armor's Current \UD will either be equal to or \DCDOWN from its \MAX. To repair your Armor, you will need the services of a Leatherworker (Light Armor) or Smith (Medium or Heavy Armor). The cost to repair armor is:

\mybullet{ 
    \item 25\FE per \UD of Light Armor repaired; 
    \item 25\AG per \UD of Medium Armor repaired; and 
    \item 10\AU per \UD of Heavy Armor repaired.  
}

These prices are \myital{per} \UD.  If you had Heavy Armor with a d8 \MAX, it would cost you 20\AU to fix it properly - 10 \AU to go from d8 to d10, and another 10 to go from d10 to d12.

