\end{multicols*}

\mysection{Traits}{monster-traits}

Monsters have specific Traits associated with them that gives them a little extra "juice" when it comes to killing Adventurers.  Some of these Traits are common to the entire \mybold{Order} (see below) that the Monster belongs to, while other Traits are specific to the Monster. 

\mytable{X X}{}{
    Acidic & Remove 1 \UD of Armor whenever the Monster deals damage. When killed: \SAVE{Toxins}. An acrid, choking plume of smoke is released. See \mypg{Acids}{malignants-acids}. \\
    Alien & Immune to Toxins and the \mypg{Secrets of Biomancy}{arcana-wizardry-secrets}. \\
    Amorphous & Immune to \mybold{Murder} (no definable anatomy). Can slip through cracks under doors, ooze up walls, hang on ceilings, etc. \\
    Amphibious & Monster can breathe on water and on land. \\
    Berserk & Monster fights until the bottom of the \mybold{next} Moment when reduced to 0 Health. \\
    Bloodthirsty & Monster can smell blood, and concentrates attacks on Adventurers who have taken Flesh damage.\\
    Cannibal & Cannibalistic Monsters can consume part of a corpse to heal 3 Health in lieu of a Combat Action.\\
    Canny & Attempts to strategize, coordinate, set traps, and ambush.\\
    Chaotic & Unhallowed. Immune to \mybold{all} Arcana except \mypg{Secrets of Entropy}{arcana-wizardry-secrets}.\\
    Dead & Unhallowed. Immune to Toxins and can only speak \mypg{Graveborn}{idiolect-graveborn}.\\
    Elemental & Immune to \mybold{all} Arcana except \mypg{Secrets of Elements}{arcana-wizardry-secrets}.\\
    Flying & Monster can spend an Action moving one range step (Close to Nearby, Nearby to Far-Away, etc.) up or down.\\
    \mylnk{Frenzied}{monster-trait-frenzied} & Monster deals +1 damage for every moment after the first (cumulative).\\
    Leaping & Jump up to 10m forward, backward, or upward. If leaping into Combat, treat as a \mybold{Charge}.\\
    Militant & Monster gets +2 on Morale tries. Will cooperate and act tactically.\\
    Mindless & Immune to \mypg{Secrets of the Mind}{arcana-wizardry-secrets}. Has no Morale, fights until it dies.\\
    Nocturnal & Can see in the dark. Adventurers get +4 bonus to Fight and Guard tries if Monster is in direct sunlight.\\
}

\newpage

\mytable{X X}{}{

    Otherworldy & Immune to damage from iron weapons.\\
    Pack & Deal +1 damage for every other Pack monster Close to them.\\
    Slippery & Cannot be Grappled, and takes 0 damage from Unarmed attacks.\\
    Spectral & Can pass through doors and walls.\\
    Splitting & Split in half if they take 7+ damage in a single attack. New Monsters have half of original's current Health (rounded up) after damange applied.\\
    Strong & Can perform feats of strength (break through chains, pick up anvils, etc.) at the Arbiter's discretion.\\
    Stupid & Easily tricked and does not strategize.\\
    Supportive & Can heal \HD Health on any Close Monster of the same species (but not themselves).\\
    Swarming & Attack \mybold{all} targets Close to them during their Action. Share Health as one pool. Unaffected by Stabbing weapons.\\
    Terrifying & Requires an \INSANITY try when the Adventurer meets them for the first time.\\
    Twitchy & Always wins Init (Pooka still beat them).\\
    Venomous & Deliver a \mypg{Noxious Toxin (d6)}{malignants-toxins} if they strike Flesh. \SAVE{Toxins} negates.\\
    \mylnk{Zoological}{monster-trait-zoological} & Considered "beasts" for the purposes of summoning, etc.\\
}




\begin{multicols*}{2}
% MONSTER TRAITS END
