% (c) 2020 Stefan Antonowicz
% Based off of tex found at https://github.com/ludus-leonis/nipajin
% This file is released under Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License.
% Please do not apply other licenses one-way.

\mysection{The Inhabitants}{the-inhabitants}

  \flavor{And within the dark circle in which the Freer stood making his curses were no unhallowed things, nor were there strangenesses such as come of night, nor whispers from unknown voices, nor sounds of any music blowing here from no haunts of men; but all was orderly and seemly there and no mysteries troubled the quiet except such as have been justly allowed to man.  And beyond that circle whence so much was beaten back by the bright vehemence of the good man's curses, the will-o'-the-wisps rioted, and many a strangeness that poured in that night from Elfland... \\~ \Tilde Lord Dunsany, \myital{The King of Elfland's Daughter} }

    The Totality is everything, and everything is the Totality. At the heart of the Totality lies the Void, and at the center of the Void grows the Tree of Ygg, and on one of the unending shoots on one of the eternal branches inside one of the trillion trillion plumules blooms a flower - the Dream. Inside the Dream \TheAuthority dreams reality, and in one dreamed universe, at an off-center point of a lenticular galaxy, there is a planet. Around this planet orbit 5 moons, and on these moons dwell the \mybold{Mortals} and the \mybold{Unseelie}, the Hallowed and the Unhallowed, the children of the Dream and the effluvium of the Void. The Mortals and Unseelie cover the five moons of Tartarus, dwelling in suspicion but relative peace, punctuated by eras of bloodshed and mayhem. 

   Mortals possess souls; all things with souls are \mybold{Hallowed}, and all Hallowed things belong to \mybold{the Dream}. Mortals are the scions of the Small Gods, the children of Order, and thus stand opposed to the Void. Any Mortal who comes in contact with the Void is swept out of the Dream, erased from time and memory.

   Curiosity is a Mortal birthright, the root of their intelligence. It is as essential to them as breath and blood. Prophets and sages, explorers and dreamers abound. Through the millennia Mortals have learned the nature of \mybold{the Great Game}, and have created \mypg{the Contract}{totality-the-contract} between themselves and their architects. They have learned that the Small Gods have souls also; they have learned that the Small Gods have something to lose; they have learned that Small Gods can die; and they have learned how they might be slain - not with the sword or arrow, but through the forgetting.\footnote{But it is no small thing to forget a God.}

    Cleverness is another inheritance, and through this shrewdness the Mortals have learned to manipulate the Void, refracting it through the Dream via \mypg{the Four Cruces}{four-cruces} - Blood, Faith, Knowledge, and Mojo - to create \mypg{the Arcana}{arcana}. The Cruces translate the echoes of the Void as vibrations in the blood and shared mythologies; as the written words of madmen, or whispered incantations born on a wind that unravels reality.

    The Unseelie do not possess a soul; all things without souls are \mybold{Unhallowed}, and all Unhallowed beings belong to \mybold{the Void}. So long as the Void exists, the Unseelie exist. The Unseelie fall into the Dream through the tatters where reality thins\footnote{\mybold{Elfland} and \mypg{the Veins of the Earth}{atlas-veins-earth}, for instance.}; they are captives of the Dream but not a part of it, alien to reality. The Unseelie are prisoners: treated with fear, suspicion, and dread by many and with kindness, pity, and understanding by few. Their connection to the Void is innate, as much a part of them as breath or thought. Eternal are the Unseelie, living outside of time and unable to die except through mischance or misfortune. 


Much ink has been spilt in philosophy and theory concerning the existence of the Unseelie. Are they part of some cosmic equation? Are Mortals judged by how they treat them? Are they a mistake? A rounding error? Or are they the great sorrow of \TheAuthority, the heart-stopping ache of a loneliness no Mortal could understand, and could never endure?
