\mysection{Overview}{civilization-overview}


Thirty-thousand years ago, your ancestors stopped their incessant wanderings and settled onto farms, which grew to cities, and civilizations.  A dozen-score empires have risen and fallen on the faces of the Five Dwarfs beneath the baleful amethyst eye of Tartarus, each successive generation (re)building on the broken bones of the before.  The detritus of the past dots the faces of the moons: not just physically in ruined buildings and destroyed palaces, but socially, spiritually, and morally.  The infection of this decay seeps into your everyday life.  You are a cargo cult of a cargo cult stumbling in the shadow of titans.

This briar patch of remnants makes it very dangerous to live outside of civilized settlements.  Cities, towns, and hamlets ooze like fungus here and there between forgotten crypts, feral ecosystems, abandoned cities, and rotting technology. Multiple vast empires of Unseelie fight and die in the Veins of the Earth beneath the surface of the moons.  Mortals huddle together in their "civilizations", hoping the campfires keep the wolves at bay.

Where the Dream is thin, the Void seeps in - and chaos reins.  Two of these places are mentioned in this book - the Veins of the Earth, and Elfland.

Murks hail from a deep place in the \myanchor{Veins of the Earth}{atlas-veins-earth}, the sunless empire that exists in the hearts of the five moons of Tartarus. Place entrances to the Veins throughout your world: in deep cracks of the earth, hidden in simple root cellars, at the bottom of deep mines, etc. 

\ed{The Veins of the Earth are a creation of Patrick Stuart and used with his permission. You should 100\% pick up a copy of this book if you don't have it already!}

Spriggan are "born" in \myanchor{Elfland}{atlas-elfland}, which should either be a large forested area in your world, or else exist "beyond Mortal ken." They say any creature foolish enough to leave Elfland will never find their way home.

\ed{Elfland is a creation of Lord Dunsany. If you haven't read "the King of Elfland's Daughter", you're missing out!}

Each of the moons of Tartarus has their own idea of what civilization means, but they generally have the following beliefs:


\mysubsection{Mortals and Unseelie}{mortals-and-unseelie}

  Mortals and Unseelie get along for the most part - particularly Mortal Adventurers, who appreciate what the Unseelie bring to the Band - but region-to-region, things might be different.  Violence against Unseelie is \myital{extremely} rare; the Mortal reaction to them is more mistrust or downright fear than anything else.

\ed{If you're familiar with the 80s/90s TV show \myital{Alien Nation}, play it like the human reaction to the Newcomers.  If you haven't seen it: imagine a race of extremely powerful aliens landed on Earth. They seem peaceful, but are much stronger, faster, and smarter than we are.  They begin moving into our neighborhoods and getting jobs, trying to integrate with us - but can never quite seem to "mesh" or overcome the humans' fear of them.  This manifests in various ways, from microaggressions to (rarely) downright violence.}

Pooka are generally the most universally accepted (\myital{everyone} likes them, after all) and Night Children run a distant second (they \myital{seem} harmless), but the immortal Rom - Spriggan and \Murk - are seen as deeply alien and ... unsettling.

Relationships between Mortal and Unseelie are also rare, but not unheard of, particularly among the Rom.  To the best knowledge of scholars, no offspring ever result from such a union - but life finds a way ...

  \mysubsection{Magic and Arcana}{magic-and-arcana}
  
  Magic is ubiquitous, necessary, and greatly feared.  It is not even remotely understood by Unseelie and Mortals alike; Unseelie because it would be like trying to examine your own brain, and Mortals because they are fucking with something powerful in usual stupid Mortal fashion.  For the average person, trucking with witches, chymists, and leeches is necessary but generally avoided (since the payment often exceeds the price), and a sorcerer moving into the ruined keep near your village would cause hushed meetings among the elders in the dead of night.  Magic is Chaos, after all - and Chaos can cause all sorts of evil if unchecked.  It is no wonder that the more Magic is present, the more the average folk turn toward the Small Gods for protection.


  \mysubsection{Religion and Mystics}{religion-and-mystics}

  Mortals accept all Small Gods in equal measure; no Small God stands above any other.  The Small Gods either exist, or they are Forgotten.

  Some Small Gods have larger followings in certain civilizations and settlements than others, but all religions are tolerated (warfare among the followers of Small Gods happens, of course - but this is to destroy the heretics rather than delegitimize what they worship).  Atheists exist - they are said to worship the Small God of No Gods - and are equally tolerated. 

  Since the Small Gods fear to become Forgotten, proselytizing is extremely common.  Churches often hire hadji, pilgrims, minstrels, and bards to go out and "spread the word" of their Small God, or pay proxies to perform the sacred rites important to the Small God so they can be free to pursue ... other entertainments.  Adventurers will meet many of these wanderers in their travels, and (when times are tight) can earn pay working for these churches themselves.


  \mysubsection{Drugs}{drugs}

\ed{Need to say this:  if you or someone you love has a problem with drugs and you're in the United States, you can call 1-800-662-HELP (4357) which is the \href{SAMHSA Hotline}{https://www.samhsa.gov/find-help/national-helpline}.  Someone out here (me!) gives a shit about you and wants you to be happy. Now, get back to the nihilism and mayhem ...}
  
  Drug use is extremely common; there seems to be no limit to what Mortals and Unseelie alike are willing to inhale, insufflate, drink, rub, lick, eat, inject or otherwise engage in creative anatomical techniques to get narcotics into their bloodstreams.  Drug use is almost never illegal, and drug dens (usually run by Pooka) are common in almost every settlement where folks gather in groups.  There are two sides to drug use of course; sanitariums, chemists, and hedge mages often stand side-by-side with these dens, ready to assist those who have taken too much, or are desperate for relief from their addiction.

