\end{multicols*}

\mysection{Curses}{cunning-curses}

Curses can be broken by the cunning folk who have placed them; by employing the services of a \mypg{Mundunugu}{gear-services}; by the miracle of \mypg{Sin Eating}{miracle-sin-eating}; or by feeding them to a \mypg{Hekaphage}{occultism-hekaphage} (provided you know the ritual, of course). Pooka are immune to curses. 

These are just a few ideas to get you started; the devious Arbiter is encouraged to concoct her own!


  \mysubsection{Lesser Curses}{table-lesser-curses}

  \mytable{l X} {  
  } {
    1 & All of your hair immediately falls off in a pile on the floor, and won't grow back. \\
    2 & You can't enter a house or cross a threshold without the permission of someone already inside. \\
    3 & You can't cross running water (even over a bridge) unless someone carries you. \\
    4 & You sprout thick, white hair from the palms of your hands and your ears.  Close observation shows very tiny translucent crabs that make their home in the strands.  No one wants to shake your hand, but cats love licking up the crabs. \\
    5 & You are unable to speak your own name \\
    6 & The Arbiter gives you a new name.  Everyone (except you) thinks this is your real name, and you can't change their mind. \\
    7 & You become Unseelie (and therefore gain \effect{Unhallowed}). \\
    8 & Like a Spriggan, you can't hold anything made of Iron.  If you do, you take 1 point of damage directly to Flesh every Moment. \\
    9 & A small imp appears on your shoulder. The imp is played by the Arbiter, and causes no end of mischief.  You can slap, step on, stab, etc. the imp, who immediately disappears with a pop - but returns in Minutes.  Angry. \\
    10 & You fall into deep slumber when you hear music. You can only be woken by being shaken / slapped awake. \\
    11 & Everything you say is believed to be a lie \\
    12 & You can only speak in rhymes. \\
}



  \mysubsection{Greater Curses}{table-greater-curses}


  \mytable{l X} {  
  } {

    1 & Leaden. Your limbs become leaden and weighty, and now have a \mylink{Burden}{gear-burden} of 4. \\
    2 & Unhanded. Roll a d6. 1-3 Your non-dominant hand disappears. 4-5 Your dominant hand disappears. 6 They both disappear. \\
    3 & Poverty. You are unable to hold coins of any sort.  Handing you any coins makes the coins disappear, permanently. \\
    4 & Dyslexia. You cannot read written words (including from a \mylink{Grimoire}{grimoires}). \\
    5 & Blindness. Your eyes disappear from your face. You are \effect{Blinded}. \\
    6 & Deafness. Your ears disappear from your head. You are \effect{Deafened}. \\
    7 & Triskaidekaphobia. For any die you roll, if you roll a 13, treat it as a natural 1. \\
    8 & Vampiric. The sun burns and blisters your skin, doing 1 Flesh damage for every Moment in direct sunlight. You cannot regain Grit unless you first drink the blood of a living thing (not enough to kill them, about a cupful). \\
    9 & Ghastly. You can't add the result of a \mylink{Personality}{adventurer-personality} try to any \RO or \RB attempt. \\
    10 & Excommunicated. You suffer from \effect{Anathema}. \\
    11 & Noisy. When you are sneaking around, you have an uncontrollable urge to sing "Here Comes a Sneaky Boy!" at top volume (regardless of gender).  Stealth is impossible. \\
    12 & Voiceless. Your vocal cords are paralyzed and you cannot speak. \\
}

\begin{multicols*}{2}
