%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Marvels
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\mysection{Marvels}{cunning-marvels}

\flavor{"Terrific, a Six Demon Bag. Sensational. What's in it Egg?" \\~"Wind! Fire!  All that kind of thing!"  \\~ \Tilde Jack Burton and Egg Shen \\~ Big Trouble in Little China}

    \mytable{Y Y} {
        \thead{\# Pips} & \thead{Coin per Pip} \\
    } {
        1-5 & 100\FE \\
        6-10 & 100\AG \\
        11+ & 100\AU
    }


\myemph{Marvels take Weeks to create}




Ornately carved scrimshaw; shruken, leathery heads; straw stuffed poppets and crystal balls.  Marvels are magical baubles, knickknacks, and trinkets imbued with drops of the Void and bound to the Dream with a Mystic's Cunning.


Marvels must be created from materials that are special or remarkable in some way. For example:

\mybullet {
  \item A carved branch of a tree that only grows in the cold stone ruins of Carcosa;
  \item 3 jeweled eggs stolen from a Roc's nest when the Eye of Tartarus is full;
  \item The carved fingerbones of St. Sacrastine, which reside in the sacristy of the Temple of Gomorrah in Lankhmar;
  \item etc.
}

Final OK is up to the Arbiter. Once you have the item, you spend your Cunning pips during Downtime to imbue it with a few drops of the Void. Each Marvel must have a \mypg{Witch Mark}{occultism-witch-mark} on it for every unique power that it has (at the Arbiter's discretion).  The most common Marvels are listed below, but feel free to create your own.



\cbreak

\callout {
    If you're creating your own Marvel, tell the Arbiter what you want it to do, and she'll respond with the cost in Cunning Pips as well as any special ingredients it might require. The Arbiter gets the final OK. Additionally, Marvels follow the following rules:

    \mybullet {
      \item They cannot be used to deal direct damage, or be an item that causes damage directly (knives, swords, etc);
      \item They cannot be used to create a \DCUP or \DCDOWN effect;
      \item They cannot duplicate the effect of any Aracana or Vulgate; and
      \item They cannot provide more than +4 to a specific \RO or \RB attempt.
    }
}



\mysubsection{Common Marvels}{cunning-common-marvels}

\MARVELS[
  Name=Adder's Tongue,
  Link=marvels-adders-tongue,
  Pips=2+
]

A single necklace of pierced adders' tongues, dipped in gold. Each tongue requires 2 Cunning to enchant, and allows the wearer to read and write one  \mypg{Language}{civilization-languages}. The Adventurer decides which languages the tongue(s) are attuned to when they put on the necklace.


\MARVELS[
  Name=Bezoar,
  Link=marvels-bezoar,
  Pips=4+
]

Super-gross mass of stuff, usually shoved into a pocket or carried in a small bag. The Bezoar provides +1 (4 Cunning Pips), +2 (8 Cunning Pips), +3 (12 Cunning Pips), or +4 (16 Cunning Pips) to Saves vs. Toxins.

\MARVELS[
  Name=Bone Abacus,
  Link=marvels-bone-abacus,
  Pips=2+
]

Adventurer's who use the Bone Abacus to do their calculations receive a +1 (2 Cunning Pips), +2 (4 Cunning Pips), +3 (6 Cunning Pips), or +4 (8 Cunning Pips) to their \mybold{Skill: Math} tries.

\MARVELS[
  Name=Bracelets of Muleskin,
  Link=marvels-bracelets-muleskin,
  Pips=1+
]

Hairy grey wristbands of muleskin, etched with runes.  The Adventurer increases their possible Burden by +1 for each Cunning Pip spent.


\MARVELS[
  Name=Cat's Paw,
  Link=marvels-cats-paw,
  Pips=2+
]

A feline paw, typically worn hanging from a string or chain around the neck. If the wearer chooses, they can "burn" one of the "lives" that resides inside the Cat's Paw, allowing them to immediately succeed on a \DEATH try without rolling. The wearer must choose to use the power of the Cat's Paw \myital{instead of} rolling their \DEATH. The Cat's Paw contains 1 "life" in it for every 2 Cunning Pips spent.

There is a catch. If you choose to use a Cat's Paw when there are no lives left inside of it, you \myital{immediately} perish. If a Cat's Paw is found as part of a treasure haul, the Arbiter should roll a d10 in secret to determine how many lives are left (rolling a 10 means the Cat's Paw has no power inside of it, and will kill anyone foolish enough to try to use it). The \mypg{Third Eye Charm}{vulgate-charms}; the Virtue of Feyness (\mypg{Mystic}{adv-mystic-feyness} or \mypg{Spriggan}{adv-spriggan-feyness}); or the Spriggan Virtue of \mypg{The Eye}{adv-spriggan-the-eye} can tell you how many lives remain inside the paw.


\MARVELS[
  Name=Cornicello,
  Link=marvels-cornicello,
  Pips=4+
]

A twisted, horn-shaped charm made from bone, terracotta, or red coral and worn as a necklace or hung from a bracelet. The Cornicello provides +1 (4 Cunning Pips), +2 (8 Cunning Pips), +3 (12 Cunning Pips), or +4 (16 Cunning Pips) to Saves vs. Doom.

\cbreak

\MARVELS[
  Name=Cornucopia,
  Link=marvels-cornucopia,
  Pips=4
]

The horn of plenty will produce enough food and water to feed the entire Band during a Bivouac (no one needs to roll a Provisions \UD).  You need to place the Cornucopia on a flat surface for it to work - but it can't be placed on the ground.

\MARVELS[
  Name=Fish Mask,
  Link=marvels-fish-mask,
  Pips=2
]

An iron mask vaguely resembling some sort of aquatic creature.  When worn, the Adventurer may breathe underwater as if they were breathing normal air (unfortunately, breathing normal air is the same as trying to breathe water).


\MARVELS[
  Name=Forbidden Fruit,
  Link=marvels-forbidden-fruit,
  Pips=8
]

You create the "perfect" fruit - a shiny and ripe apple; a thick pomegranate; a juicy orange; etc. If proferred to someone, the victim must Save vs. Hexes or be compelled to take a bite. Once a bite is taken from the fruit, its enchantment ends. Toxins can be injected into the fruit via syringe, if desired.


\MARVELS[
  Name=Golden Ankh,
  Link=marvels-ankh,
  Pips=8
]

The Golden Ankh is usually fastened with a cord and worn as a necklace, but it can also be an earring, hung from a belt, etc. The Adventurer in possession of an Ankh only fails their \DEATH try if they roll a 1 (instead of a 1 or a 2).

\MARVELS[
  Name=Hammerspace Bag,
  Link=marvels-hammerspace-bag,
  Pips=2+
]

A sack or satchel made of spidersilk, the \mybold{Hammerspace Bag} can store a few kg of insignificant items (Arbiter's discretion) and/or a number of significant items with a Burden equal to the Cunning Pips spent. The objects are stored in \mylink{Hammerspace}{meta-hammerspace}. Whatever you're looking for is always at the top of the bag.  Turning the bag upside down and shaking it will cause everything to fall out.

\MARVELS[
  Name=Ivory Earnhorn,
  Link=marvels-ivory-earhorn,
  Pips=2+
]

When the ivory earhorn is held up to the ear, the Adventurer gains a +1 (2 Cunning Pips), +2 (4 Cunning Pips), +3 (6 Cunning Pips), or +4 (8 Cunning Pips) to their \mybold{Skill: Listen} tries.


\MARVELS[
  Name=Lucky Horseshoe,
  Link=marvels-lucky-horseshoe,
  Pips=2+
]

A rusty horseshoe with a four-leaf clover embossed at the base, the Adventurer holding it receives a +1 (2 Cunning Pips), +2 (4 Cunning Pips), +3 (6 Cunning Pips), or +4 (8 Cunning Pips) to their \mybold{Skill: Travel} tries.


\MARVELS[
  Name=Lucky Rabbit's Foot,
  Link=marvels-lucky-rabbits-foot,
  Pips=8
]

An usually large rabbit's foot with a silver cap on one end. Those in possession of a Lucky Rabbit's Foot only fail their \INJURY try if they roll a 1 (instead of a 1 or a 2). You probably shouldn't show this to a Pooka, they get pretty upset ...


\MARVELS[
  Name=Magic Jar,
  Link=marvels-magic-jar,
  Pips=12
]

An enchanted oil lamp / jar of stoneware / palm-sized iron box / stoppered bottle / etc. marked with runes. By Concentrating for Minutes, a Mortal Adventurer in possession of the Magic Jar may remove their soul and seal it inside. The Adventurer may at any time remove the soul from the container and place it back "inside" themselves by again Concentrating for Minutes.

There's only room for one soul inside the Magic Jar. A Mortal Adventurer can only restore their own soul and no one else's.  Any time they remove or restore their soul from the Magic Jar, they must make an \INSANITY try. Adventurers who have had their souls removed take on \effect{Unhallowed}. If the Mortal is killed while their soul is inside of the Magic Jar, their body flashes immediately out of existence (as if they were Unseelie) and their soul becomes an \mypg{Unquiet Spirit}{monster-unquiet-spirit} (an Apparition, Spook, Phantom, or Ghost depending on how powerful they were in life. See the Bestiary under \mypg{Monsters}{monsters} for more info). This spirit is trapped inside of the Magic Jar, and will burst forth in a terrible anger as soon as the oil lamp is rubbed, stoneware is broken, or box is opened.

An Unseelie may remove the soul stored in the Magic Jar and place it in themselves, removing the \effect{Unhallowed} (and making them immune to Curse the Unhallowed, allowing them to enter Hallowed Ground, etc.). If an Unseelie dies while possessed by a Mortal soul, it immediately departs to the Void and drags the soul with it for an eternity of torment.

Losing a Magic Jar with your soul in it is ... bad. Mystical creatures and demons often use souls as bargaining chips, trades, "ingredients", etc. and will pay a good price for a Mortal soul. 



\MARVELS[
  Name=Mermaid's Scale,
  Link=marvels-mermaids-scale,
  Pips=2+
]

The scale is from the area near the waist, and marred with black runes. When held, the Adventurer gains a +1 (2 Cunning Pips), +2 (4 Cunning Pips), +3 (6 Cunning Pips), or +4 (8 Cunning Pips) to their \mybold{Skill: Salt} tries.

\newpage

\MARVELS[
  Name=Poppet,
  Link=marvels-poppet,
  Pips=1+
]

A little rag doll or sock puppet, the Poppet will absorb a number of \mypg{Secrets of the Mind}{arcana-wizardry-secrets-alignment} equal to the number of Cunning Pips spent in its creation. When the Poppet absorbs the last effect, it falls apart. The owner of the Poppet will know if a Secret is cast on them, and whether or not the Poppet absorbed its effect.

\MARVELS[
  Name=Scrying Vessel,
  Link=marvels-scrying-vessel,
  Pips=4
]

Orbuculums, magic mirrors, crystal balls, etc. - a necessary bit of equipment for those wishing to practice \mypg{Descrying}{occultism-descry}.

\MARVELS[
  Name=Seer's Pipe,
  Link=marvels-seers-pipe,
  Pips=2+
]

When smoked with \mylink{Pipeweed}{gear-narcotics-pipeweed}, the Adventurer receives a +1 (2 Cunning Pips), +2 (4 Cunning Pips), +3 (6 Cunning Pips), or +4 (8 Cunning Pips) to their \mybold{Skill: Lore} tries (on top of the bonus for the Pipeweed).

\MARVELS[
  Name=Shrunken Head,
  Link=marvels-shrunken-head,
  Pips=8
]

Usually hung from the belt, an Adventurer in possession of a Shrunken Head only fails their \INSANITY try if they roll a 1 (instead of a 1 or a 2).



\MARVELS[
  Name=Silver Bolt,
  Link=marvels-silver-bolt,
  Pips=2
]

A holly-branch missile with a silver tip, the Silver Bolt deals +d4 damage against Unhallowed creatures, and +3d4 damage against \mypg{the Damned}{forgotten-fealty-damned}. 

\cbreak

\MARVELS[
  Name=Silver Monocle,
  Link=marvels-silver-monocle,
  Pips=2+
]

If any Adventurer firmly grips the Silver Monocle in their eyesocket, they receive a +1 (2 Cunning Pips), +2 (4 Cunning Pips), +3 (6 Cunning Pips), or +4 (8 Cunning Pips) to their \mybold{Skill: Eyeball} tries.

 
\MARVELS[
  Name=Talisman,
  Link=marvels-talisman,
  Pips=4+
]

A parchment, small knife, flat disc, etc. inscribed with runes. The Talisman provides +1 (4 Cunning Pips), +2 (8 Cunning Pips), +3 (12 Cunning Pips), or +4 (16 Cunning Pips) to \SAVE{Hexes}.


\MARVELS[
  Name=Voodoo Doll,
  Link=marvels-voodoo-doll,
  Pips=12
]

A cloth, wax, or wooden doll with a simple yet somehow gruesome visage. By holding the Voodoo doll in front of yourself and concentrating on one Close or Nearby Monster (or Ally) that is wounded, you inflict them with \effect{Bleeding} for as long as you Concentrate. You must mumble constantly while Concentrating - not loud, but not a whisper either.

\MARVELS[
  Name=Witch Bottle,
  Link=marvels-witch-bottle,
  Pips=2
]

A greybeard or bellarmine made of stoneware, glazed with salt, and embossed with a bearded face. Used to store \mypg{Unhallowed Earth}{occultism-unhallowed-earth}.


\MARVELS[
  Name=Wolf Tooth,
  Link=marvels-wolf-tooth,
  Pips=2+
]

If pressed into an empty tooth socket, the Wolf Tooth binds to the gums and the Adventurer receives a +1 (2 Cunning Pips), +2 (4 Cunning Pips), +3 (6 Cunning Pips), or +4 (8 Cunning Pips) to their \mybold{Skill: Bushcraft} tries.


