\end{multicols*}
\mysection{The Crux of Mojo}{cruces-mojo}

\flavor{
    Some walked the earth as witches, proud daughters of Khauran, with the moon of hell burning upon their ivory bosoms. Each was named Salome. I too am Salome. It was always Salome, the witch. It will always be Salome, the witch, even when the mountains of ice have roared down from the pole and ground the civilizations to ruin, and a new world has risen from the ashes and dust—even then there shall be Salomes to walk the earth, to trap men's hearts by their sorcery, to dance before the kings of the world, to see the heads of the wise men fall at their pleasure. \\~ \Tilde Robert E. Howard. "A Witch Shall Be Born"
    }


Mortals are the purpose of the Dream; the reason for its existence. Mortals alone can unlock Its true power. These mysteries are passed down through the ages, mother to daughter, stretching back to the very beginning. The essence of the Dream can be heard singing in the rivers and whispering through the leaves; it can be felt when a baby is pulled from the womb; it can be seen in the reading of entrails and in the patterns of the smokes; it can be heard in the songs of crickets. The Dream is here for Mortal use - anyone, from king to mudlark, can harness it for weal or woe. Only the dead can look backwards and tell  you what they have seen, and give those clever enough the prudence of countless lifetimes.

By mastering the Crux of Mojo, you learn the wisdom of \mybold{Witchcraft} to divine auguries and manipulate the dead using your \mybold{Juju}.


  \mysubsection{Juju}{cruces-mojo-juju}

    \begin{center}
        \myemph{Your Juju starts at d4}
    \end{center}



Your Juju is a \UD that represents the potency of the materials you have on you to perform \mypg{Arcana:Witchcraft}{arcana-witchcraft}.  As your \UD moves \DCDOWN, the potency fades - fresh blood must be applied, incantations of renewal must be recited, herbs must be gathered, etc.  You start with a \UDD{d4}, but can increase this die through \mypg{Advancement}{advancement}.

Your \MAX Juju also affords you a certain "rank" among the poor and uneducated, who will treat you with respect or fear.  They will refer to you using this honorific ("Go see the Herbalist", for example, or screaming "the Necromancer!" before fleeing in terror).

\myctrtable{Y Y}{
      \thead{Honorific} & \thead{Juju} \\
    }{
      "Herbalist" & d4  \\
      "Wisdom" & d6  \\
      "Witch" & d8  \\
      "Necromancer" & d10  \\
    }

\begin{multicols*}{2}


