\end{multicols*}
\mysection{Creation}{adventurer-creation}

\flavor{
    Between the time when the oceans drank Atlantis, and the rise of the sons of Aryas, there was an age undreamed of. And unto this, Conan, destined to wear the jeweled crown of Aquilonia upon a troubled brow. \\~ \Tilde \mybold{Conan the Barbarian}
}

Fate has something in store for you.

Maybe you're a hunter who stumbled into a life on the run. Maybe you're a Spriggan who fell in love with a Mortal, following him and leaving behind Elfland forever. Perhaps you're a torturer turned combat doctor. Whatever your humble beginnings, you are now something else. Something different.

You are an \mybold{Adventurer}.

Rather than eking out a living tanning hides or digging up potatoes, you've decided to take what you desire from the Wilds. Tombs, crypts and catacombs dot the unsettled parts of your world; dungeons and vaults hide beneath misty barrows on the downs; haunted pyramids and castles beckon the unwary and foolish; and beneath it all lie \mylink{The Veins of the Earth}{murk-veins-of-the-earth}, full of unknown treasures. Power lies inside them all - power through wealth, power through influence, power that defies Order and bends reality to its will. 

Adventurers favor alliances, forming caravans, companies, and expedition parties to travel into the unknown to seek their fortune. You and your \mylink{Band}{roles-band} of like-minded Adventurers will risk everything to break the bonds of a simple fate, to become kings and queens by your own hand.


\mysubsection{Building Your Adventurer}{adventurer-building}

Building your Adventurer is fairly straightforward. Grab the \mylink{Basic Adventurer Sheet}{adventurer-sheet.1} in the appendix and:

\callout {
\mybullet {
    \item Assign a d8 to each aspect of your \mylink{Identity}{adventurer-identity} (Vigor, Dexterity, Intelligence, and Focus)
    \item Assign a d4 to each aspect of your \mylink{Personality}{adventurer-personality} (Presence, Talent, Awareness, and Clarity)
    \item Assign a d3 to each aspect of your \mylink{Kismet}{adventurer-kismet} (Death, Injury, and Insanity)
    \item Assign a d4 to each one of your \mylink{Saves}{adventurer-saves} (Hexes, Toxins, and Doom), \mybold{then pick one of these Saves and make it a d8+1}
    \item Assign a d4 to each one of your \mylink{Skills}{adventurer-skills} (Bushcraft, Eyeball, Listen, Lore, Math, Salt, and Travel), \mybold{then pick one of these Skills and make it a d8+1}
}

}

Once you're done there, decide if you want to play a \mylink{Mortal Trope}{adventurer-tropes} (Sellsword, Knave, Philosopher, or Mystic) or an \mylink{Unseelie Species}{adventurer-species} (Murk, Pooka, Night Child, or Spriggan). Grab the appropriate \mylink{Trope Character Sheet}{adventurer-sheet.3} or \mylink{Species Character Sheet}{adventurer-sheet.7} from the appendix, flip to the appropriate section of the book, and follow the creation instructions. Depending on your choices, you'll modify both your sheets (including writing down your \mylink{Flesh}{adventurer-flesh-grit} and \mylink{Grit}{adventurer-flesh-grit}).

Fill out your name and the name of your Band, grab your dice and a cold beverage, and get ready to hit the dungeon / crypt / skull of dead god / abandoned derelict spaceship / etc.


\newpage
\begin{multicols*}{2}\raggedcolumns

